I am grateful to Scott and Mira for their endless patience, encouragement, support, and wisdom. Thank you for believing in my research even when I didn't. When I first visited UCSD, Scott took me for a walking meeting through the gorgeous eucalyptus forest. Not only was this a genius recruiting tactic, it gave me a first glimpse into his unique approach to research, communication, and life. I've learned so much more from Scott than I realize even now, and am ever grateful for the tight-knit community he fostered in our lab and amongst his students. Mira and I first met in a North Toronto coffee shop, and she has continued to awe and inspire me ever since with her incredible mind, generous heart, and endless passion for her work. It has been such a joy to work with Mira and I could not be more excited to continue doing so at Adobe. I'm rarely sure of anything in my life, but I am sure that this next step is exactly where I want to go.

I am lucky to have such a talented and supportive committee. Thanks to Jim for always giving me such positive and encouraging feedback and guidance, and always being open to a chat. Thanks to Philip for reminding me why my research is exciting when I lose steam, and for so much valuable advice over the years. Thank you to Bill for many stimulating conversations about research, photography, and life. And finally, thanks to Björn for guiding my work with insightful questions and thoughtful feedback.

The Design Lab and CSE Department have both fostered wonderful communities that I am grateful to be a part of. I am thankful to Don Norman for his leadership of the Design Lab and for welcoming me on that first day back in 2014 when I shyly walked into the lab. Thank you to the many members of the Design Lab who have given me so much valuable feedback. Thanks to Julia and James for being such wonderful mentees and collaborators, and for giving me the joy of seeing their passion for research grow. Thanks to Ian, Vanessa, Sara, Olga, and the entire Design Lab operations team past and present, for their indispensable support. And Teenah, who has supported me with her endless generosity since the very start: it's been a delight to learn and grow alongside you. Thank you to Julie for always keeping me on track, and for the many quick meetings that turned into long conversations. 
I am grateful for funding from UCSD's Powell Fellowship, NSERC, Adobe Research, and the CSE Department.


I could not have gotten through this journey without an incredible support system of labmates, collaborators, and friends. Thank you to Cat for patiently teaching me the ropes and welcoming me with open arms into your San Diego world. Thank you to Vineet, Tricia, Ariel, and the rest of the crewtons for sushiboocha, coffee breaks, tea time, naps in the lab, late night deadline companionship, and everything else. Thank you Vineet for paving the way ahead, keeping my spirits up in our windowless office, and testing all your good (and bad) jokes on me. I'll always remember those three magical months when we got to work in the office with windows. Tricia, my two-time-award-winning co-author, thank you for keeping me sane through our research projects (especially the studies) and for always being awkward with me. Thank you Amy for all our adventures, and for the world's best napping chair. Thank you Tiffany for your life-changing support throughout this journey, and Vivian for going above and beyond in your care.

Thank you Ariana for being an exceptional roommate, friend, and colleague, and for your endless support and energy. In the time you have been here, you have transformed not only my life, but also GradWIC and the entire CSE Department. Thanks to all those who have contributed to GradWIC for helping us build an important and ever-growing community. Thank you to the many aerial friends and mentors I've made at UCSD and AR, especially Chava and her Angells, for getting me in better shape (physically and mentally) than I've ever been. Thank you Diana for following me to San Diego (sorry I'm leaving now) and including me in all your family adventures. Thank you Chris for growing with me this entire way, supporting me through the worst times, and celebrating with me in the best times. You make me a better person, and I can't wait to continue this adventure together.

I am grateful to Adobe and Autodesk for supporting me through four summer internships. To have spent one summer reading all of Tovi Grossman and George Fitzmaurice's papers, and then the following summer writing a paper with both of them was an absolute dream. I am grateful to have worked with and learned from so many exceptional researchers: Joel Brandt, Joy Kim, Valentina Shin, Holger Winnemöller, Sheryl Ehrlich, Andy Wilson, Alison Thornsberry, Fraser Anderson, and others. Thanks to the many fellow interns I've shared these experiences with, especially the Miracles (Yea-Seul, Jasper, Amanda, Daniel) and my Canadian buddies, David and Rahul. Thanks to Minsuk, who I've somehow never actually done an internship with but who was never too far away. Possibly one of the most successful meetups enabled by Confer! Thanks to Jordana, Rachel, and Willy for the luckiest summer roommate situation.

Diane Horton's passion for teaching and constant encouragement is what first got me interested in Computer Science, and for that I will be forever grateful. Thanks also to Karen Reid and Paul Gries for their incredible teaching and mentorship. Thank you to Kyros Kutulakos and Matt O'Toole for showing me how to do good research. Thank you to my former office-mate and soon-to-be colleague Peter O'Donovan for introducing me to HCI and to Scott's research.

And finally, thanks to my family. To my mother Nancy for all the crucial stats help, my father Don for telling people I was doing a PhD before I'd even decided to, my sister Donelle for her never-ending kindness and generosity, and of course Sammy and Tibby.
\\

\textsc{Chapter \ref{chapter:replay}}, in part, includes portions of material as it appears in \textit{RePlay: Contextually Presenting Learning Videos Across Software Applications} by C. Ailie Fraser, Tricia J. Ngoon, Mira Dontcheva, and Scott Klemmer in the Proceedings of the 2019 CHI Conference on Human Factors in Computing Systems (CHI '19). The dissertation author was the primary investigator and author of this paper.

\textsc{Chapter \ref{chapter:remap}}, in part, is currently being prepared for submission for publication of the material. C. Ailie Fraser, Julia M. Markel, N. James Basa, Mira Dontcheva, and Scott Klemmer. The dissertation author was the primary investigator and author of this material.

\textsc{Chapter \ref{chapter:liveclips}}, in part, includes portions of material as it appears in \textit{Sharing the Studio: How Creative Livestreaming can Inspire, Educate, and Engage} by C. Ailie Fraser, Joy O. Kim, Alison Thornsberry, Scott Klemmer, and Mira Dontcheva in the Proceedings of the 2019 on Creativity and Cognition (C\&C '19). The dissertation author was the primary investigator and author of this paper.

\textsc{Chapter \ref{chapter:liveclips}}, in part, includes portions of material coauthored with Andy Edmonds and Mira Dontcheva. The dissertation author was the primary investigator and author of this material.

\textsc{Chapter \ref{chapter:discoveryspace}}, in part, includes portions of material as it appears in \textit{DiscoverySpace: Suggesting Actions in Complex Software} by C. Ailie Fraser, Mira Dontcheva, Holger Winnemöller, Sheryl Ehrlich, and Scott Klemmer in the Proceedings of the 2016 ACM Conference on Designing Interactive Systems (DIS '16). The dissertation author was the primary investigator and author of this paper.

\textsc{Chapter \ref{chapter:critiquekit}}, in part, includes portions of material as it appears in \textit{Interactive Guidance Techniques for Improving Creative Feedback} by Tricia J. Ngoon, C. Ailie Fraser, Ariel S. Weingarten, Mira Dontcheva, and Scott Klemmer in the Proceedings of the 2018 CHI Conference on Human Factors in Computing Systems (CHI '18). The dissertation author was one of the primary investigators and authors of this paper.

\textsc{Appendix \ref{chapter:appendix}}, in part, includes portions of material as it appears in \textit{Sharing the Studio: How Creative Livestreaming can Inspire, Educate, and Engage} by C. Ailie Fraser, Joy O. Kim, Alison Thornsberry, Scott Klemmer, and Mira Dontcheva in the Proceedings of the 2019 on Creativity and Cognition (C\&C '19). The dissertation author was the primary investigator and author of this paper.