\begin{vita}
  \item[2013] Honours B.Sc. with High Distinction, Specialist in Math \& Computer Science, Major in Music, University of Toronto, Canada
  \item[2016] M.S. in Computer Science, University of California San Diego
  \item[2020] Ph.~D. in Computer Science, University of California San Diego
\end{vita}
\begin{publications}
\item C. Ailie Fraser, Joy Kim, Valentina Shin, Joel Brandt, and Mira Dontcheva. 2020. Temporal Segmentation of Creative Live Streams. To appear in \textit{Proceedings of the 2020 CHI Conference on Human Factors in Computing Systems (CHI '20)}.
\item C. Ailie Fraser, Mira Dontcheva, Joy O. Kim, and Scott Klemmer. 2019. How live streaming does (and doesn't) change creative practices. \textit{interactions} 27, 1 (December 2019), 46–51.
\item C. Ailie Fraser, Joy O. Kim, Alison Thornsberry, Scott Klemmer, and Mira Dontcheva. 2019. Sharing the Studio: How Creative Livestreaming can Inspire, Educate, and Engage. In \textit{Proceedings of the 2019 on Creativity and Cognition (C\&C '19)}. Association for Computing Machinery, New York, NY, USA, 144–155.
\item C. Ailie Fraser, Tricia J. Ngoon, Mira Dontcheva, and Scott Klemmer. 2019. RePlay: Contextually Presenting Learning Videos Across Software Applications. In \textit{Proceedings of the 2019 CHI Conference on Human Factors in Computing Systems (CHI '19)}. Association for Computing Machinery, New York, NY, USA, Paper 297, 1–13.
\item Tricia J. Ngoon, C. Ailie Fraser, Ariel S. Weingarten, Mira Dontcheva, and Scott Klemmer. 2018. Interactive Guidance Techniques for Improving Creative Feedback. In \textit{Proceedings of the 2018 CHI Conference on Human Factors in Computing Systems (CHI '18)}. Association for Computing Machinery, New York, NY, USA, Paper 55, 1–11.
\item C. Ailie Fraser, Tovi Grossman, and George Fitzmaurice. 2017. WeBuild: Automatically Distributing Assembly Tasks Among Collocated Workers to Improve Coordination. In \textit{Proceedings of the 2017 CHI Conference on Human Factors in Computing Systems (CHI '17)}. Association for Computing Machinery, New York, NY, USA, 1817–1830.
\item C. Ailie Fraser, Mira Dontcheva, Holger Winnemöller, Sheryl Ehrlich, and Scott Klemmer. 2016. DiscoverySpace: Suggesting Actions in Complex Software. In \textit{Proceedings of the 2016 ACM Conference on Designing Interactive Systems (DIS '16)}. Association for Computing Machinery, New York, NY, USA, 1221–1232.
\item Catherine M. Hicks, Vineet Pandey, C. Ailie Fraser, and Scott Klemmer. 2016. Framing Feedback: Choosing Review Environment Features that Support High Quality Peer Assessment. In \textit{Proceedings of the 2016 CHI Conference on Human Factors in Computing Systems (CHI '16)}. Association for Computing Machinery, New York, NY, USA, 458–469.
\end{publications}