\chapter{DiscoverySpace: Suggesting Actions in Complex Software}
\label{chapter:discoveryspace}
\begin{quote}
When using complex software for the first time, sometimes even video assistance can be too overwhelming. RePlay and ReMap found that people don't always know what help to search for to achieve their goal, and novices may not even know what goals are possible. LiveClips proposed contextual examples to help users explore potential outcomes, but it does not help them \textit{achieve} these outcomes. Even when following tutorials, novices often get lost in the many steps required to achieve their goals. To address these challenges, this chapter introduces \textit{Discovery\-Space}, a contextual panel for Adobe Photoshop that suggests action macros to apply to photographs. Discovery\-Space harvests these one-click actions from the online Photoshop user community. A between-subjects study indicated that action suggestions may help novices maintain confidence, accomplish tasks, and discover features. This work demonstrates how interfaces can leverage user-generated content to help novices achieve expert-level outcomes in complex software.
\end{quote}

\input{discoveryspace/1_intro}
\input{discoveryspace/2_related_work}
\input{discoveryspace/3_formative_study}
\input{discoveryspace/4_design_goals}
\input{discoveryspace/5_system}
\input{discoveryspace/6_study}
\input{discoveryspace/7_discussion}
\input{discoveryspace/8_future_work}
\input{discoveryspace/9_conclusion}

\section{Acknowledgements}
We thank Nancy Reid \& Catherine Hicks for their help with statistical analyses. This work was supported in part by a Powell Fellowship from UC San Diego.

This chapter, in part, includes portions of material as it appears in \textit{DiscoverySpace: Suggesting Actions in Complex Software} by C. Ailie Fraser, Mira Dontcheva, Holger Winnemöller, Sheryl Ehrlich, and Scott Klemmer in the Proceedings of the 2016 ACM Conference on Designing Interactive Systems (DIS '16). The dissertation author was the primary investigator and author of this paper.