\chapter{CritiqueKit: Interactive Guidance Techniques for Improving Creative Feedback}
\label{chapter:critiquekit}
\begin{quote}
All of the systems presented so far have aimed to support people doing creative tasks in complex software. But with creative tasks, the software is not always the only complex part. Creative tasks can themselves be complex and difficult by virtue of being subjective and open-ended. One example of such a task is giving feedback. Good feedback is critical to creativity and learning, but many people do not know how to actually \textit{provide} effective feedback. This chapter contributes empirical evidence that two interactive techniques – reusable suggestions and adaptive guidance – can help people provide better feedback on creative work. We present these techniques embodied in the \textit{CritiqueKit} system to help reviewers give specific, actionable, and justified feedback. Two real-world deployment studies and two controlled experiments with CritiqueKit found that adaptively-presented suggestions improve the quality of feedback from novice reviewers.
\end{quote}

\input{critiquekit/1_intro}
\input{critiquekit/2_related_work}
\input{critiquekit/3_system}
\input{critiquekit/4_deployments}
\input{critiquekit/5_experiments}
\input{critiquekit/6_discussion}
\input{critiquekit/7_conclusion}

\section{Acknowledgements}
We thank Kandarp Khandwala and Janet Johnson for help rating feedback. This research was supported in part by a fellowship from Adobe Research.

This chapter, in part, includes portions of material as it appears in \textit{Interactive Guidance Techniques for Improving Creative Feedback} by Tricia J. Ngoon, C. Ailie Fraser, Ariel S. Weingarten, Mira Dontcheva, and Scott Klemmer in the Proceedings of the 2018 CHI Conference on Human Factors in Computing Systems (CHI '18). The dissertation author was one of the primary investigators and authors of this paper.
