
% % Load basic packages
% \usepackage{balance}       % to better equalize the last page
% \usepackage{graphics}      % for EPS, load graphicx instead 
% \usepackage[T1]{fontenc}   % for umlauts and other diaeresis
% \usepackage{txfonts}
% \usepackage{mathptmx}
% \usepackage[pdflang={en-US},pdftex]{hyperref}
% \usepackage{color}
% \usepackage{booktabs}
% \usepackage{textcomp}

% % Some optional stuff you might like/need.
% \usepackage{microtype}        % Improved Tracking and Kerning
% % \usepackage[all]{hypcap}    % Fixes bug in hyperref caption linking
% \usepackage{ccicons}          % Cite your images correctly!
% % \usepackage[utf8]{inputenc} % for a UTF8 editor only

% If you want to use todo notes, marginpars etc. during creation of
% your draft document, you have to enable the "chi_draft" option for
% the document class. To do this, change the very first line to:
% "\documentclass[chi_draft]{sigchi}". You can then place todo notes
% by using the "\todo{...}"  command. Make sure to disable the draft
% option again before submitting your final document.
% \usepackage{todonotes}
\chapter{ReMap: Multimodal Help-Seeking}
\label{chapter:remap}
\begin{quote}
People are reluctant to search for help when they feel it will take more time than trial-and-error exploration, even with a contextual search system like RePlay. However, trial-and-error often takes a long time or does not result in a correct solution. Given this cognitive bias, how might we lower the barrier to searching for help? This chapter aims to make searching easier and faster through multimodal interaction. We introduce \textit{ReMap}, an extension to the RePlay system that allows users to speak search queries, adding app-specific terms deictically. Users can navigate ReMap's search results via speech or mouse. A lab study showed that ReMap helped people stay focused on their task while simultaneously searching for and using help resources. Users' experiences with ReMap also raised a number of important challenges with incorporating multimodal features into a help-seeking system.
\end{quote}

\input{remap/intro}
\input{remap/related_work}
\input{remap/system}
\input{remap/study}
\input{remap/discussion}
\input{remap/conclusion}
